---
title: "1-Initial data screening"
author: "Will Sheppard"
date: "2022-11-11"
output: html_document
---
This script will screen for any inconsistencies that mean a participant may need to be excluded from the study - ACQ errors, Double check that no U18s have participated etc.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(data.table)
```
## read in online data

this chunk sets the working directory and then imports the seperate data files for the demographics questionaire, the combined vision tests and the debrief.
the debrief is extracted to allow the prize to be given.

```{r online data}
setwd('../data/onlineNorway')

demoOnline <- read.csv('./data_exp_102468-v2_questionnaire-gb9f.csv')
emailOnline <- read.csv('./data_exp_102468-v2_questionnaire-mq5s.csv')

# read in all task files and combine into a single DF for vision tests
# use this once all files have data in
#files = list.files(pattern="*task*")
bigFiles <- file.info(list.files(pattern="*task*")) %>%
  filter(size > 2000)
files <- rownames(bigFiles)
#files = 
visionTestsOnline = do.call(rbind, lapply(files, fread))
rm(files)
rm(bigFiles)

visionTestsOnline <- as.data.frame(unclass(visionTestsOnline))

length(unique(visionTestsOnline$Participant.Public.ID))
```

Not all participants completed the online session on a pc/tablet as asked
```{r pc}
pcPP <- demoOnline %>%
  filter(Participant.Device.Type != 'mobile')%>%
  select(Participant.Public.ID)

pcPP <- as.list(pcPP$Participant.Public.ID)



visionTestsOnline <- visionTestsOnline %>%
  filter(Participant.Public.ID %in% pcPP)


# how many were excluded?
notPC <- demoOnline %>%
  filter(Participant.Device.Type == 'mobile')%>%
  select(Participant.Public.ID)
notPC <- length(unique(notPC$Participant.Public.ID))

```

`r notPC` were excluded for using a mobile rather than PC or laptop or tablet

# let's import the lab collected data for the online tests
```{r lab data}
setwd('../data/labNorway')

demoLab <- read.csv('./data_exp_102467-v5_questionnaire-u67w.csv')
emailLab <- read.csv('./data_exp_102467-v5_questionnaire-mq5s.csv')

# create list of chart files
chartFiles <- c("data_exp_102467-v5_task-fwvh.csv", "data_exp_102467-v5_task-ysdh.csv")
preTest <- 'data_exp_102467-v5_task-4atu.csv'

# read in all task files and combine into a single DF for vision tests
# use this once all files have data in
#files = list.files(pattern="*task*")
bigFiles <- file.info(list.files(pattern="*task*")) %>%
  filter(size > 2000)

bigFiles$name <- rownames(bigFiles) 

bigFiles <- bigFiles %>%
  filter(!name %in% chartFiles)%>%
  filter(name != preTest)
files <- row.names(bigFiles)


#files = 
# why is this not working?!
visionTestsLab = do.call(rbind, lapply(files, fread))
rm(files)
rm(bigFiles)

visionTestsLab <- as.data.frame(unclass(visionTestsLab))

```

```{r merge v4 files}
setwd('../data/labNorway/v4')



demoLab_v4 <- read.csv('./data_exp_102467-v4_questionnaire-u67w.csv')
emailLab_v4 <- read.csv('./data_exp_102467-v4_questionnaire-mq5s.csv')


# create list of chart files
chartFiles_v4 <- c("data_exp_102467-v4_task-fwvh.csv", "data_exp_102467-v4_task-ysdh.csv")
preTest_v4 <- 'data_exp_102467-v4_task-4atu.csv'

# read in all task files and combine into a single DF for vision tests
# use this once all files have data in
#files = list.files(pattern="*task*")
bigFiles_v4 <- file.info(list.files(pattern="*task*")) %>%
  filter(size > 2000)

bigFiles_v4$name <- rownames(bigFiles_v4)

bigFiles_v4 <- bigFiles_v4 %>%
  filter(!name %in% chartFiles_v4)%>%
  filter(name != preTest_v4)
files_v4 <- row.names(bigFiles_v4)


visionTestsLab_v4 = do.call(rbind, lapply(files_v4, fread))
rm(files_v4)
rm(bigFiles_v4)

visionTestsLab_v4 <- as.data.frame(unclass(visionTestsLab_v4))
```
```{r bind v4 and v5}
visionTestsLab <- rbind(visionTestsLab, visionTestsLab_v4)
```




```{r select response rows}
visionTestsOnline <- visionTestsOnline %>%
  filter(Zone.Type == 'response_text_entry') %>%
  rename(id = Participant.Public.ID)

visionTestsLab <- visionTestsLab%>%
  filter(Zone.Type == 'response_text_entry')%>%
  rename(id = Participant.Public.ID)

```


how many participants did we start with?
```{r participants}

labPPS <- unique(visionTestsLab$id)
onlinePPS <- unique(visionTestsOnline$id)

length(which(onlinePPS %in% labPPS))
length(which(labPPS  %in% onlinePPS))

visionTestsLab <- visionTestsLab %>%
  filter(id %in% onlinePPS)

visionTestsOnline <- visionTestsOnline %>%
  filter(id %in% labPPS)

```

Participant 7 got the answer right but also typed in the question, include
Participant 30 got an ACQ question wrong in both sessions, exclude - excluded by previous step
participant 48 got the acq wrong in the online session, with shorter RT and worse performance, exclude.- excluded by previous step
```{r ACQ check}
acqOnline <- visionTestsOnline %>%
  filter(display == 'ACQ')
acqLab <- visionTestsLab %>%
  filter(display == 'ACQ')

#which partiicpants got this wrong?
acqOnlineWrong <- acqOnline %>%
  filter(Incorrect == 1)
acqLabWrong <- acqLab %>%
  filter(Incorrect == 1)%>%
  filter(id != 7)

# create a list of participants who got these questions wrong
acqA <- as.list(acqOnlineWrong$id)
acqB <- as.list(acqLabWrong$id)

acqWrong <- c(acqA, acqB)
```

```{r acq removal}
acqWrong <- unique(acqWrong)

visionTestsLab <- visionTestsLab %>%
  filter(!id %in% acqWrong)
visionTestsOnline <- visionTestsOnline %>%
  filter(!id %in% acqWrong)

length(unique(visionTestsLab$id))
```

remove all participants not included in CS data
```{r cs removal, eval=FALSE}

csPP <- read.csv("../data/csPPS.csv")
csPP <- as.list(csPP$id)

visionTestsLab <- visionTestsLab %>%
  filter(id %in% csPP)
visionTestsOnline <- visionTestsOnline %>%
  filter(id %in% csPP)
```

So therefore we now have a sample of `r length(unique(visionTestsLab$id))` participants

extract the order in which the participants did the tasks
```{r order effects}
onlineDates <- visionTestsOnline %>%
  select(id, UTC.Timestamp) %>%
  group_by(id) %>%
  summarise(timeStampOnline = first(UTC.Timestamp))

labDates <- visionTestsLab %>%
  select(id, UTC.Timestamp) %>%
  group_by(id) %>%
  summarise(timeStampLab = first(UTC.Timestamp))

dates <- full_join(onlineDates, labDates, by = "id") %>%
  mutate(onlineFirst = case_when(
    timeStampOnline < timeStampLab ~ 1,
    TRUE ~ 0
  ))

sum(dates$onlineFirst)
```

```{r save data}
write.csv(visionTestsLab, "../data/visionTestsLab.csv")
write.csv(visionTestsOnline, "../data/visionTestsOnline.csv")
write.csv(dates, "../data/sessionOrder.csv")
```