---
title: "2. CS data cleaning"
author: "Will Sheppard"
date: "2022-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

# import functions
source('functions_visionProcessing_and_threshEstimation.R')
```


```{r read data}
csOnline <- read.csv("../data/visionTestsOnline.csv")%>%
  filter(display == 'cs')
csLab <- read.csv("../data/visionTestsLab.csv")%>%
  filter(display == 'cs')
csChart <- read.csv("../data/visualTestData.csv")%>%
  select(id, csChart)
```

```{r shorten CS}
csShortOnline <- shortenCS(csOnline)
csShortLab <- shortenCS(csLab)
```


Within a participant and within a contrast level, there is a negative relationship between response time and correctness.
This suggests that removing responses with a particularly long response time may improve accuracy

mean correlation between response time and correctness for both lab and online recruitment is -0.12 both of which are significantly different to 0. 

t tests show that the correlations beare sig. different 
```{r does RT predict correct, eval=FALSE}
rtOnlineMod <- glm(Correct ~ id + contrast + responseTime, 
                   data = csShortOnline,
                   family = 'binomial')

rtLabMod <- glm(Correct ~ id + contrast + responseTime, 
                   data = csShortLab,
                   family = 'binomial')

summary(rtOnlineMod)
summary(rtLabMod)

```



```{r create summary data frames}
csSummOnline <- summShortCS(csShortOnline)

csSummLab <- summShortCS(csShortLab)
```



```{r save data}
write.csv(csSummLab, "../data/csSummLab.csv")
write.csv(csSummOnline, "../data/csSummOnline.csv")
```
