---
title: "vaPsychoFunction"
author: "Will Sheppard"
date: "2023-08-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(quickpsy)
```

read data 
```{r read data}
data <- read.csv("../data/vaSummLab.csv")%>%
  select(-X, -meanResponseTime)
onlineData <- read.csv("../data/vaSummOnline.csv")%>%
  select(-X, -meanResponseTime)
```

psychometric fucnitons fit more consistantly is the full parameter space is full
i.e. paticipants need a percCorrect value for all logMAR values from 1.0 to -0.2
all participants start at 1.0, so the top end is not the issue
therefore, we need to create a row for each unsampled level for each participant
these will need a percCorrect of 0, therefore, 1 attempt and 0 correct
participants 3 and 4 online are good examples
```{r fill parameter online space}

pplist <- unique(onlineData$id)
xMIN <- -0.2
onlineAllLevels <- data.frame(matrix(
  data = NA,
  ncol = ncol(onlineData),
  nrow =  0
))

for (pp in pplist) {
  d <- onlineData %>%
    filter(id == pp)
  pp <- first(d$id)
  minLogMAR <- min(d$logMAR)
  
  #print(pp)
  #print(minLogMAR)
  
  if(minLogMAR < (xMIN+0.1)){
    #print(paste("pp:", pp,": none missing", sep = ""))
    onlineAllLevels <- rbind(onlineAllLevels, d)
  }else{
    
    #print(paste("pp:", pp,": levels missing", sep = ""))
    missingLevels <- seq(xMIN, min(d$logMAR)-0.1, 0.1)
    #print(paste("missing:", missingLevels, sep = ""))
    
    newDF <- data.frame(matrix(
      data = NA,
      nrow = length(missingLevels),
      ncol = ncol(d)
      ))
    
    colnames(newDF) <- colnames(d)
    newDF$id <- first(d$id)
    newDF$logMAR <- missingLevels
    newDF$totalAttempt <- 1
    newDF$totalCorrect <- 0
    newDF$percCorrect <- 0
    
    newDF <- rbind(newDF, d)
    
    #print(newDF)
    onlineAllLevels <- rbind(onlineAllLevels, newDF)
    
    
  }
  

  
}



```


lets redo the modelling
```{r generic modelling}

cols <- c("id",
          "va", "vaLower", "vaUpper",
          "percCorrect","fun", "guessRate",
          "setting")



funList <- c("logistic_fun", "cum_normal_fun", "weibull_fun")
#funList <- c("weibull_fun")

denomList <- c(10, 26)

settingList <- c("Lab", "Online")

for (setting in settingList) {
  if (setting == "Lab"){
        settingData <- data
        
      }else{
        settingData <- onlineAllLevels
      }
      
      pplist <- unique(settingData$id)
      #pplist <- 1:10
      
      thresh <- data.frame(matrix(
      data = NA,
      nrow = length(pplist),
      ncol = 8))
      
      colnames(thresh) <- cols
      
      for (fun in funList) {
        for (denom in denomList) {
          for (pp in pplist) {
            
            d <- settingData %>%
              filter(id == pp)
            
            g <- 1/denom
            p <- g + .5 * (1 - g)
            
            xMIN <- min(d$logMAR)
            xMAX <- max(d$logMAR)+0.1
            
            minPercCorr = min(d$percCorrect)
            minLogMAR = min(d$logMAR)
            
            print(paste("Participant:", pp, " ", setting, "", ", ", fun, "", ", Guess rate: 1/", denom, sep = ""))
            
            if (minPercCorr < p) {
              if (fun == "logistic_fun"){
                fitOne <- quickpsy(d = d, x = logMAR, k = totalCorrect, n = totalAttempt,
                               guess = g, lapses = TRUE, bootstrap = 'nonparametric',
                               xmin = xMIN, xmax = xMAX, fun = logistic_fun)
              }else if (fun == "cum_normal_fun"){
                fitOne <- quickpsy(d = d, x = logMAR, k = totalCorrect, n = totalAttempt,
                               guess = g, lapses = TRUE, bootstrap = 'nonparametric',
                               xmin = xMIN, xmax = xMAX, fun = cum_normal_fun)
              }else if (fun == "weibull_fun"){
                
                d$logMAR <- d$logMAR+0.2
                
                xMIN <- min(d$logMAR)
                xMAX <- max(d$logMAR)+0.1
                
                fitOne <- quickpsy(d = d, x = logMAR, k = totalCorrect, n = totalAttempt,
                               guess = g, lapses = TRUE, bootstrap = 'nonparametric',
                               xmin = xMIN, xmax = xMAX, fun = weibull_fun)
              }
              
              x <- plotcurves(fitOne)+
              scale_x_continuous(limits = c(xMIN, xMAX), breaks = seq(-0.2, xMAX, 0.1))+
              scale_y_continuous(limits = c(0,1), breaks = seq(0, 1, 0.1))+
              ggtitle(paste("pp: ", pp, " - ", setting, ", ", fun, "guess rate 1/", denom))
              show(x)
            
              thresh[which(pplist == pp), 1] <- pp
              thresh[which(pplist == pp), 2] <- round(fitOne$thresholds[1], digits = 2)
              thresh[which(pplist == pp), 3] <- round(fitOne$thresholds[3], digits = 2)
              thresh[which(pplist == pp), 4] <- round(fitOne$thresholds[4], digits = 2)
              thresh[which(pplist == pp), 5] <- fitOne$thresholds[2]
              thresh[which(pplist == pp), 6] <- fun
              thresh[which(pplist == pp), 7] <- 1/denom
              thresh[which(pplist == pp), 8] <- setting
            
            } else{
              if(fun == "weibull_fun"){
                thresh[which(pplist == pp), 1] <- pp
                thresh[which(pplist == pp), 2] <- xMIN+0.2
                thresh[which(pplist == pp), 3] <- xMIN+0.2
                thresh[which(pplist == pp), 4] <- xMIN+0.2
                thresh[which(pplist == pp), 5] <- p
                thresh[which(pplist == pp), 6] <- fun
                thresh[which(pplist == pp), 7] <- 1/denom
                thresh[which(pplist == pp), 8] <- setting
              }else{
                thresh[which(pplist == pp), 1] <- pp
                thresh[which(pplist == pp), 2] <- xMIN
                thresh[which(pplist == pp), 3] <- xMIN
                thresh[which(pplist == pp), 4] <- xMIN
                thresh[which(pplist == pp), 5] <- p
                thresh[which(pplist == pp), 6] <- fun
                thresh[which(pplist == pp), 7] <- 1/denom
                thresh[which(pplist == pp), 8] <- setting
              }
              
                
            }
              
            
            
          }
          assign(paste(fun, denom, "va", setting, sep = ""), thresh)
        }
      }
  
}
```

```{r quick plots}

#put all data frames into list
df_list <- list(cum_normal_fun10vaLab, cum_normal_fun10vaOnline, cum_normal_fun26vaLab, cum_normal_fun26vaOnline,
                logistic_fun10vaLab, logistic_fun10vaOnline, logistic_fun26vaLab, logistic_fun26vaOnline,
                weibull_fun10vaLab, weibull_fun10vaOnline, weibull_fun26vaLab, weibull_fun26vaOnline)


#merge all data frames in list
modelledData <- df_list %>% 
  reduce(full_join)

modelledData <- modelledData %>%
  mutate(va = case_when(
    fun == "weibull_fun" ~ va - 0.2,
    TRUE ~ va
  ))%>%
  mutate(vaLower = case_when(
    fun == "weibull_fun" ~ vaLower - 0.2,
    TRUE ~ vaLower
  ))%>%
  mutate(vaUpper = case_when(
    fun == "weibull_fun" ~ vaUpper - 0.2,
    TRUE ~ vaUpper
  ))

wideData <- modelledData %>%
  pivot_wider(id_cols = c(id, fun, guessRate), 
              values_from = va,
              names_from = setting)
```

```{r save}

chartdata <- read.csv('../data/visualTestData.csv')%>%
  select(-csChart)
df <- merge(wideData, chartdata, by = "id") 


filePath <- paste("../data/vaThreshModelled.csv", sep = "")

write.csv(df, filePath)
#write.csv(cs, "../data/csThreshModelled10.csv")
```



there are no mising levels in the lab data, but it is worth having this here for future analysis

```{r fill parameter lab space}

pplist <- unique(data$id)

labAllLevels <- data.frame(matrix(
  data = NA,
  ncol = ncol(data),
  nrow =  0
))

for (pp in pplist) {
  d <- data %>%
    filter(id == pp)
  pp <- first(d$id)
  minLogMAR <- min(d$logMAR)
  
  #print(pp)
  #print(minLogMAR)
  
  if(minLogMAR < (xMIN+0.1)){
    #print(paste("pp:", pp,": none missing", sep = ""))
    labAllLevels <- rbind(labAllLevels, d)
  }else{
    
    #print(paste("pp:", pp,": levels missing", sep = ""))
    missingLevels <- seq(xMIN, min(d$logMAR)-0.1, 0.1)
    #print(paste("missing:", missingLevels, sep = ""))
    
    newDF <- data.frame(matrix(
      data = NA,
      nrow = length(missingLevels),
      ncol = ncol(d)
      ))
    
    colnames(newDF) <- colnames(d)
    newDF$id <- first(d$id)
    newDF$logMAR <- missingLevels
    newDF$totalAttempt <- 1
    newDF$totalCorrect <- 0
    newDF$percCorrect <- 0
    
    newDF <- rbind(newDF, d)
    
    #print(newDF)
    labAllLevels <- rbind(labAllLevels, newDF)
    
    
  }
  

  
}



```

```{r min va}

minPossVa <- onlineAllLevels %>%
  group_by(id) %>%
  dplyr::summarise(minPossVa = )
```


```{r lab first fit}
pplist <- unique(data$id)
#pplist <- 33
thresh <- data.frame(matrix(
  data = NA,
  nrow = length(pplist),
  ncol = 5))
  
cols <- c("id",
            "threshold", "percCorrect",
            "threshLower", "threshUpper")

colnames(thresh) <- cols

rm(cols)

#p = 0.5

for (pp in  pplist){
  d <- data %>%
    filter(id == pp)

  minPercCorr = min(d$percCorrect)
  minLogMAR = min(d$logMAR)
  
  print(pp)
  print(minLogMAR)
  print(minPercCorr)
  
  if (minPercCorr < p) {
    fitOne <- quickpsy(d = d, x = logMAR, k = totalCorrect, n = totalAttempt,
                     guess = guess, lapses = TRUE, bootstrap = 'nonparametric',
                     xmin = xMIN, xmax = xMAX)
  x <- plotcurves(fitOne)+
    scale_x_continuous(limits = c(xMIN, xMAX), breaks = seq(xMIN, xMAX, 0.1))+
    scale_y_continuous(limits = c(0,1), breaks = seq(0, 1, 0.1))+
    ggtitle(pp)
  show(x)
  
  thresh[which(pplist == pp), 1] <- pp
  thresh[which(pplist == pp), 2] <- fitOne$thresholds[1]
  thresh[which(pplist == pp), 3] <- fitOne$thresholds[2]
  thresh[which(pplist == pp), 4] <- fitOne$thresholds[3]
  thresh[which(pplist == pp), 5] <- fitOne$thresholds[4]
    
  } else{
    thresh[which(pplist == pp), 1] <- pp
    thresh[which(pplist == pp), 2] <- minLogMAR
    thresh[which(pplist == pp), 3] <- minPercCorr
    thresh[which(pplist == pp), 4] <- minLogMAR
    thresh[which(pplist == pp), 5] <- minLogMAR
  }
  

}

labThresh <- thresh
```


```{r online first fit}
pplist <- unique(onlineData$id)
#pplist <- 3

thresh <- data.frame(matrix(
  data = NA,
  nrow = length(pplist),
  ncol = 5))
  
cols <- c("id",
            "threshold", "percCorrect",
            "threshLower", "threshUpper")

colnames(thresh) <- cols

rm(cols)

#p = 0.5


for (pp in  pplist){
  d <- onlineAllLevels %>%
    filter(id == pp)
  
  #d <- tail %>%
  #  filter(id == pp)
  
  #dataInd <- which(d)
  
  minPercCorr = min(d$percCorrect)
  minLogMAR = min(d$logMAR)
  
  print(pp)
  print(minLogMAR)
  print(minPercCorr)
  
  if (minPercCorr < p) {
    fitOne <- quickpsy(d = d, x = logMAR, k = totalCorrect, n = totalAttempt,
                     guess = guess, lapses = TRUE, bootstrap = 'nonparametric',
                     xmin = xMIN, xmax = xMAX)
  x <- plotcurves(fitOne)+
    scale_x_continuous(limits = c(xMIN, xMAX), breaks = seq(xMIN, xMAX, 0.1))+
    scale_y_continuous(limits = c(0,1), breaks = seq(0, 1, 0.1))+
    ggtitle(pp)
  show(x)
  
  thresh[which(pplist == pp), 1] <- pp
  thresh[which(pplist == pp), 2] <- fitOne$thresholds[1]
  thresh[which(pplist == pp), 3] <- fitOne$thresholds[2]
  thresh[which(pplist == pp), 4] <- fitOne$thresholds[3]
  thresh[which(pplist == pp), 5] <- fitOne$thresholds[4]
    
  } else{
    thresh[which(pplist == pp), 1] <- pp
    thresh[which(pplist == pp), 2] <- minLogMAR
    thresh[which(pplist == pp), 3] <- minPercCorr
    thresh[which(pplist == pp), 4] <- minLogMAR
    thresh[which(pplist == pp), 5] <- minLogMAR
  }
  

}

onlineThresh <- thresh
```

```{r import chart data and merge}
chartdata <- read.csv('../data/visualTestData.csv')

lab <- labThresh %>%
  select(id, threshold) %>%
  rename(vaLab = threshold)

lab <- lab  %>%
    mutate(twoDP = as.numeric(str_sub(abs(vaLab), 4, 4)))%>% 
  replace(is.na(.), 0)%>%
    mutate(x = case_when(
      twoDP%%2 == 0 & vaLab >= 0 ~ plyr::round_any(vaLab, 0.02, f = floor),
      twoDP%%2 == 0 & vaLab < 0~ plyr::round_any(vaLab, 0.02, f = ceiling),
      twoDP%%2 == 1 & vaLab >= 0 ~ plyr::round_any(vaLab, 0.02, f = ceiling),
      twoDP%%2 == 1 & vaLab < 0 ~ plyr::round_any(vaLab, 0.02, f = floor)
    )) %>%
    select(-vaLab, -twoDP) %>%
  rename(vaLab = x)%>%
  mutate(vaLab = case_when(
    vaLab < -0.2 ~ -0.2,
    TRUE ~ vaLab
  ))

online <- onlineThresh %>%
  select(id, threshold) %>%
  rename(vaOnline = threshold)

online <- online %>%
    mutate(twoDP = as.numeric(str_sub(abs(vaOnline), 4, 4)))%>% 
  replace(is.na(.), 0)%>%
    mutate(x = case_when(
      twoDP%%2 == 0 & vaOnline >= 0 ~ plyr::round_any(vaOnline, 0.02, f = floor),
      twoDP%%2 == 0 & vaOnline < 0~ plyr::round_any(vaOnline, 0.02, f = ceiling),
      twoDP%%2 == 1 & vaOnline >= 0 ~ plyr::round_any(vaOnline, 0.02, f = ceiling),
      twoDP%%2 == 1 & vaOnline < 0 ~ plyr::round_any(vaOnline, 0.02, f = floor)
    )) %>%
    select(-vaOnline, -twoDP) %>%
  rename(vaOnline = x)%>%
  mutate(vaOnline = case_when(
    vaOnline < -0.2 ~ -0.2,
    TRUE ~ vaOnline
  ))
   

df <- merge(lab, chartdata, by = "id")
df <- merge(df, online, by = "id") %>%
  select(-csChart)

```

```{r save data}
#write.csv(labThresh, "../data/vaLabThreshModelled.csv")
#write.csv(onlineThresh, "../data/vaOnlineThreshModelled.csv")

filePath <- paste("../data/vaThreshModelled", gDenom,".csv", sep = "")

write.csv(df, filePath)
```