---
title: "6-blandAltman"
author: "Will Sheppard"
date: "2023-11-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The aim of this script is to compare the modelling of the cs and va data across the different functions and guess rates

```{r load packages}
library(tidyverse)
library(blandr)
library(ggplot2)
library(psych)
library(ggpubr)
```


```{r import and prep data}

csImport <- read.csv("../data/csThreshModelled.csv") 
vaImport <- read.csv("../data/vaThreshModelled.csv")




# change names
csName <- csImport %>%
  rename(Chart = csChart)
vaName <- vaImport %>%
  rename(Chart = vaChart)

# add guess rate to group by
csAll <- csName %>%
  mutate(gR = case_when(
    guessRate > 0.05 ~ 10,
    TRUE ~ 26)
    )
csAll$gR <- as.factor(csAll$gR)
vaAll <- vaName %>%
  mutate(gR = case_when(
    guessRate > 0.05 ~ 10,
    TRUE ~ 26)
    )
vaAll$gR <- as.factor(vaAll$gR)

# remove rows with NAs
#csNA <- na.omit(csAll)
#vaNA <- na.omit(vaAll)



# remove impossible cs values e.g. > 2 and < 0
cs <- csAll %>%
  filter(Lab <= 2 & Lab>0)%>%
  filter(Online <= 2 & Online > 0)%>%
  filter(Chart <= 1.92 & Chart|0)%>%
  filter(id != 61)
va <- vaAll %>%
  filter(Lab <= 1.1 & Lab >= -0.2)%>%
  filter(Online <= 1.1 & Online >= -0.2)%>%
  filter(Chart <= 1.1 & Chart >= -0.4) %>%
  filter(id!= 61)

weibVA <- va %>%
  filter(fun == "weibull_fun")


```

cap variables
```{r cap}

cs <- cs %>%
  mutate(Online = case_when(
    Online > 1.92 ~ 1.92,
    TRUE ~ Online
  ))%>%
  mutate(Lab = case_when(
    Lab > 1.92 ~ 1.92,
    TRUE ~ Lab
    ))
va <- va %>%
  mutate(Chart = case_when(
    Chart < -0.2 ~ -0.2,
    TRUE ~ Chart
    ))
```

csBA stats
```{r csBA}

funList <- as.list(unique(cs$fun))
gList <- as.list(unique(cs$guessRate))

genericDF <- data.frame(matrix(
  data = NA,
  ncol = 13,
  nrow =  length(funList)*length(gList)
))


names <- c("funciton", "guessRate",
           "bias", "biasLower", "biasUpper",
           "lowerLOA", "lowerLOA_lowerCI", "lowerLOA_upperCI",
           "upperLOA", "upperLOA_lowerCI", "upperLOA_upperCI",
           "percHighdiff", "ciWidth")

colnames(genericDF) <- names

chartLab <- genericDF
chartOnline <- genericDF
labOnline <- genericDF

p <- 0.95
row <- 0

for (f in funList) {
  for (g in gList) {
    
    d <- cs %>%
      filter(fun == f)%>%
      filter(guessRate == g)
    
    
    
    row <- row + 1
    
    
    chartLab[row, 1] <- f
    chartLab[row, 2] <- g
    chartLab[row, 3] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$bias, digits = 2)
    chartLab[row, 4] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$biasLowerCI, digits = 2)
    chartLab[row, 5] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$biasUpperCI, digits = 2)
    chartLab[row, 6] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$lowerLOA, digits = 2)
    chartLab[row, 7] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$lowerLOA_lowerCI, digits = 2)
    chartLab[row, 8] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$lowerLOA_upperCI, digits = 2)
    chartLab[row, 9] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$upperLOA, digits = 2)
    chartLab[row, 10] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$upperLOA_lowerCI, digits = 2)
    chartLab[row, 11] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$upperLOA_upperCI, digits = 2)
    chartLab[row, 12] <- round((sum(abs(blandr.statistics(d$Chart, d$Lab, sig.level = p)$differences) > .15)/length(blandr.statistics(d$Chart, d$Lab, sig.level = p)$differences))*100, digits = 2)
    chartLab[row, 13] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$upperLOA - blandr.statistics(d$Chart, d$Lab, sig.level = p)$lowerLOA, digits = 2)
    
    CL <- blandr.draw(d$Chart, d$Lab)+
      ggtitle(paste("Chart v Lab. Function: ", f, ", guess rate: 1/", 1/g, sep = "" ))
      
    show(CL)
    
    chartOnline[row, 1] <- f
    chartOnline[row, 2] <- g
    chartOnline[row, 3] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$bias, digits = 2)
    chartOnline[row, 4] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$biasLowerCI, digits = 2)
    chartOnline[row, 5] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$biasUpperCI, digits = 2)
    chartOnline[row, 6] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$lowerLOA, digits = 2)
    chartOnline[row, 7] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$lowerLOA_lowerCI, digits = 2)
    chartOnline[row, 8] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$lowerLOA_upperCI, digits = 2)
    chartOnline[row, 9] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$upperLOA, digits = 2)
    chartOnline[row, 10] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$upperLOA_lowerCI, digits = 2)
    chartOnline[row, 11] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$upperLOA_upperCI, digits = 2)
    chartOnline[row, 12] <- round((sum(abs(blandr.statistics(d$Chart, d$Online, sig.level = p)$differences) > .15)/length(blandr.statistics(d$Chart, d$Online, sig.level = p)$differences))*100, digits = 2)
    chartOnline[row, 13] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$upperLOA - blandr.statistics(d$Chart, d$Online, sig.level = p)$lowerLOA, digits = 2)
    
    CO <- blandr.draw(d$Chart, d$Online)+
      ggtitle(paste("Chart v Online. Function: ", f, ", guess rate: 1/", 1/g, sep = "" ))
      
    show(CO)
    
    labOnline[row, 1] <- f
    labOnline[row, 2] <- g
    labOnline[row, 3] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$bias, digits = 2)
    labOnline[row, 4] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$biasLowerCI, digits = 2)
    labOnline[row, 5] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$biasUpperCI, digits = 2)
    labOnline[row, 6] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$lowerLOA, digits = 2)
    labOnline[row, 7] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$lowerLOA_lowerCI, digits = 2)
    labOnline[row, 8] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$lowerLOA_upperCI, digits = 2)
    labOnline[row, 9] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$upperLOA, digits = 2)
    labOnline[row, 10] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$upperLOA_lowerCI, digits = 2)
    labOnline[row, 11] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$upperLOA_upperCI, digits = 2)
    labOnline[row, 12] <- round((sum(abs(blandr.statistics(d$Lab, d$Online, sig.level = p)$differences) > .15)/length(blandr.statistics(d$Lab, d$Online, sig.level = p)$differences))*100, digits = 2)
    labOnline[row, 13] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$upperLOA - blandr.statistics(d$Lab, d$Online, sig.level = p)$lowerLOA, digits = 2)
    
    LO <- blandr.draw(d$Lab, d$Online)+
      ggtitle(paste("Lab v Online. Function: ", f, ", guess rate: 1/", 1/g, sep = "" ))
      
    show(LO)
    
    
  }
  
}

```


We are basing the decision on the chart v online comparisons as this is most similar to what we want to use the test for
```{r plot final cs}

csStats <- data.frame(matrix(
  data = NA,
  ncol = 13,
  nrow =  3
))


names <- c("setting", "funciton", "guessRate",
           "bias", "biasLower", "biasUpper",
           "lowerLOA", "lowerLOA_lowerCI", "lowerLOA_upperCI",
           "upperLOA", "upperLOA_lowerCI", "upperLOA_upperCI",
           "point15diff")

colnames(csStats) <- names

csFinal <- cs %>%
  filter(fun == "weibull_fun")%>%
  filter(gR == "26")

csCO <- blandr.statistics(csFinal$Chart, csFinal$Online, sig.level = p)
csCL <- blandr.statistics(csFinal$Chart, csFinal$Lab, sig.level = p)
csLO <- blandr.statistics(csFinal$Lab, csFinal$Online, sig.level = p)


csStats[1, 1] <- "chart v online"
csStats[1, 2] <- "weibull_fun"
csStats[1, 3] <- "26"
csStats[1, 4] <- round(csCO$bias, digits = 2)
csStats[1, 5] <- round(csCO$biasLowerCI, digits = 2)
csStats[1, 6] <- round(csCO$biasUpperCI, digits = 2)
csStats[1, 7] <- round(csCO$lowerLOA, digits = 2)
csStats[1, 8] <- round(csCO$lowerLOA_lowerCI, digits = 2)
csStats[1, 9] <- round(csCO$lowerLOA_upperCI, digits = 2)
csStats[1, 10] <- round(csCO$upperLOA, digits = 2)
csStats[1, 11] <- round(csCO$upperLOA_lowerCI, digits = 2)
csStats[1, 12] <- round(csCO$upperLOA_upperCI, digits = 2)
csStats[1, 13] <- round((sum(abs(csCO$differences) > .15)/length(csCO$differences))*100, digits = 2)

csStats[2, 1] <- "chart v lab"
csStats[2, 2] <- "weibull_fun"
csStats[2, 3] <- "26"
csStats[2, 4] <- round(csCL$bias, digits = 2)
csStats[2, 5] <- round(csCL$biasLowerCI, digits = 2)
csStats[2, 6] <- round(csCL$biasUpperCI, digits = 2)
csStats[2, 7] <- round(csCL$lowerLOA, digits = 2)
csStats[2, 8] <- round(csCL$lowerLOA_lowerCI, digits = 2)
csStats[2, 9] <- round(csCL$lowerLOA_upperCI, digits = 2)
csStats[2, 10] <- round(csCL$upperLOA, digits = 2)
csStats[2, 11] <- round(csCL$upperLOA_lowerCI, digits = 2)
csStats[2, 12] <- round(csCL$upperLOA_upperCI, digits = 2)
csStats[2, 13] <- round((sum(abs(csCL$differences) > .15)/length(csCL$differences))*100, digits = 2)

csStats[3, 1] <- "lab v online"
csStats[3, 2] <- "weibull_fun"
csStats[3, 3] <- "26"
csStats[3, 4] <- round(csLO$bias, digits = 2)
csStats[3, 5] <- round(csLO$biasLowerCI, digits = 2)
csStats[3, 6] <- round(csLO$biasUpperCI, digits = 2)
csStats[3, 7] <- round(csLO$lowerLOA, digits = 2)
csStats[3, 8] <- round(csLO$lowerLOA_lowerCI, digits = 2)
csStats[3, 9] <- round(csLO$lowerLOA_upperCI, digits = 2)
csStats[3, 10] <- round(csLO$upperLOA, digits = 2)
csStats[3, 11] <- round(csLO$upperLOA_lowerCI, digits = 2)
csStats[3, 12] <- round(csLO$upperLOA_upperCI, digits = 2)
csStats[3, 13] <- round((sum(abs(csLO$differences) > .15)/length(csLO$differences))*100, digits = 2)

csMaxDiff <- max(c(max((csCL$differences)), max((csCO$differences)), max((csLO$differences))  ) )
csMinDiff <- min(c(min((csCL$differences)), min((csCO$differences)), min((csLO$differences))  ) )-0.05

csMaxMean <- max(c(max((csCL$means)), max((csCO$means)), max((csLO$means))  ) )
csMinMean <- min(c(min((csCL$means)), min((csCO$means)), min((csLO$means))  ) )

csXmin <- -Inf
csXmax <- Inf

csCO_BA <- blandr.draw(csFinal$Chart, csFinal$Online,
                       ciShading = FALSE, ciDisplay=TRUE, plotter = "ggplot")+
  ylim(csMinDiff, csMaxDiff)+
  xlim(csMinMean, csMaxMean)+
  theme_bw()+ 
  #labs(tag = "A")+
  theme(
    plot.title = element_blank()
    )+ 
  geom_rect(aes(xmin= csXmin, xmax= csXmax, ymin= csCO$biasLowerCI, ymax= csCO$biasUpperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= csXmin, xmax= csXmax, ymin= csCO$lowerLOA_lowerCI, ymax= csCO$lowerLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= csXmin, xmax= csXmax, ymin= csCO$upperLOA_lowerCI, ymax= csCO$upperLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)

csCL_BA <- blandr.draw(csFinal$Chart, csFinal$Lab,
                       ciShading = FALSE, ciDisplay=TRUE, plotter = "ggplot")+
  ylim(csMinDiff, csMaxDiff)+
  xlim(csMinMean, csMaxMean)+
  theme_bw()+
  #labs(tag = "B")+
  theme(
    plot.title = element_blank()
    )+ 
  geom_rect(aes(xmin= csXmin, xmax= csXmax, ymin= csCL$biasLowerCI, ymax= csCL$biasUpperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= csXmin, xmax= csXmax, ymin= csCL$lowerLOA_lowerCI, ymax= csCL$lowerLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= csXmin, xmax= csXmax, ymin= csCL$upperLOA_lowerCI, ymax= csCL$upperLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)

csLO_BA <- blandr.draw(csFinal$Lab, csFinal$Online,
                       ciShading = FALSE, ciDisplay=TRUE, plotter = "ggplot")+
  ylim(csMinDiff, csMaxDiff)+
  xlim(csMinMean, csMaxMean)+
  theme_bw()+
  #labs(tag = "C")+
  theme(
    plot.title = element_blank()
    )+ 
  geom_rect(aes(xmin= csXmin, xmax= csXmax, ymin= csLO$biasLowerCI, ymax= csLO$biasUpperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= csXmin, xmax= csXmax, ymin= csLO$lowerLOA_lowerCI, ymax= csLO$lowerLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= csXmin, xmax= csXmax, ymin= csLO$upperLOA_lowerCI, ymax= csLO$upperLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)



# csPlot <- ggarrange(
#   csCO_BA + xlab("Mean CS score (log units)") + ylab("Clinical v OU \n CS score difference (log units)"), 
#           #NULL,
#   csCL_BA + xlab("Mean CS score (log units)") + ylab("Clinical v OSS \n CS score difference (log units)"), 
#           #NULL,
#   csLO_BA + xlab("Mean CS score (log units)") + ylab("OSS v OS \n CS score difference (log units)"),
#           ncol = 1,
#           #heights = c(1, -0.2, 1, -0.2, 1),
#           labels = c("A", "B", "C"),
#           align = "hv")

library(ggeasy)

margins <- c(0, 0.2, 0, 0.8)
bottomMargin <- c(0, 0.2, 0.2, 0.8)

csPlot <- ggarrange(
  csCO_BA + ylab("Clinical v OU \n CS score difference (log units)") + 
    theme(axis.title.x = element_blank(), plot.margin = unit(margins, 'lines')), 
  csCL_BA + ylab("Clinical v OSS \n CS score difference (log units)") + 
    theme(axis.title.x = element_blank(), plot.margin = unit(margins, 'lines')), 
  csLO_BA + ylab("OSS v OS \n CS score difference (log units)") + xlab("Mean CS score (log units)") + 
    theme(plot.margin = unit(bottomMargin, 'lines')),
          ncol = 1,
          labels = c("A", "B", "C"),
          align = "hv")

show(csPlot)

```

SAVE THE PARTICIPANTS WHO APPEAR IN THE CS DATA and remove all others from va data 
```{r cs participants}

ppList <- unique(cs$id)

vaPps <- va %>%
  filter(id %in% ppList)

```


vaBA stats
```{r vaBA}

funList <- as.list(unique(vaPps$fun))
gList <- as.list(unique(vaPps$guessRate))

genericDF <- data.frame(matrix(
  data = NA,
  ncol = 14,
  nrow =  length(funList)*length(gList)
))


names <- c("funciton", "guessRate",
           "bias", "biasLower", "biasUpper",
           "lowerLOA", "lowerLOA_lowerCI", "lowerLOA_upperCI",
           "upperLOA", "upperLOA_lowerCI", "upperLOA_upperCI",
           "point2diff", "point1diff", "ciDiff")

colnames(genericDF) <- names

vaChartLab <- genericDF
vaChartOnline <- genericDF
vaLabOnline <- genericDF

p <- 0.95
row <- 0

for (f in funList) {
  for (g in gList) {
    
    d <- vaPps %>%
      filter(fun == f)%>%
      filter(guessRate == g)
    
    
    
    row <- row + 1
    
    
    vaChartLab[row, 1] <- f
    vaChartLab[row, 2] <- g
    vaChartLab[row, 3] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$bias, digits = 2)
    vaChartLab[row, 4] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$biasLowerCI, digits = 2)
    vaChartLab[row, 5] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$biasUpperCI, digits = 2)
    vaChartLab[row, 6] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$lowerLOA, digits = 2)
    vaChartLab[row, 7] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$lowerLOA_lowerCI, digits = 2)
    vaChartLab[row, 8] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$lowerLOA_upperCI, digits = 2)
    vaChartLab[row, 9] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$upperLOA, digits = 2)
    vaChartLab[row, 10] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$upperLOA_lowerCI, digits = 2)
    vaChartLab[row, 11] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$upperLOA_upperCI, digits = 2)
    vaChartLab[row, 12] <- round((sum(abs(blandr.statistics(d$Chart, d$Lab, sig.level = p)$differences) > .2)/length(blandr.statistics(d$Chart, d$Lab, sig.level = p)$differences))*100, digits = 2)
    vaChartLab[row, 13] <- round((sum(abs(blandr.statistics(d$Chart, d$Lab, sig.level = p)$differences) > .1)/length(blandr.statistics(d$Chart, d$Lab, sig.level = p)$differences))*100, digits = 2)
    #vaChartLab[row, 14] <- round(blandr.statistics(d$Chart, d$Lab, sig.level = p)$upperLOA - blandr.statistics(d$Chart, d$Lab, sig.level = p)$lowerLOA, digits = 2)

    vaCL <- blandr.draw(d$Chart, d$Lab)+
      ggtitle(paste("Chart v Lab. Function: ", f, ", guess rate: 1/", 1/g, sep = "" ))
      
    show(vaCL)
    
    vaChartOnline[row, 1] <- f
    vaChartOnline[row, 2] <- g
    vaChartOnline[row, 3] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$bias, digits = 2)
    vaChartOnline[row, 4] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$biasLowerCI, digits = 2)
    vaChartOnline[row, 5] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$biasUpperCI, digits = 2)
    vaChartOnline[row, 6] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$lowerLOA, digits = 2)
    vaChartOnline[row, 7] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$lowerLOA_lowerCI, digits = 2)
    vaChartOnline[row, 8] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$lowerLOA_upperCI, digits = 2)
    vaChartOnline[row, 9] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$upperLOA, digits = 2)
    vaChartOnline[row, 10] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$upperLOA_lowerCI, digits = 2)
    vaChartOnline[row, 11] <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$upperLOA_upperCI, digits = 2)
    vaChartOnline[row, 12] <- round((sum(abs(blandr.statistics(d$Chart, d$Online, sig.level = p)$differences) > .2)/length(blandr.statistics(d$Chart, d$Online, sig.level = p)$differences))*100, digits = 2)
    vaChartOnline[row, 13] <- round((sum(abs(blandr.statistics(d$Chart, d$Online, sig.level = p)$differences) > .1)/length(blandr.statistics(d$Chart, d$Online, sig.level = p)$differences))*100, digits = 2)
    #vaChartOnline <- round(blandr.statistics(d$Chart, d$Online, sig.level = p)$upperLOA - blandr.statistics(d$Chart, d$Online, sig.level = p)$lowerLOA, digits = 2)
    
    vaCO <- blandr.draw(d$Chart, d$Online)+
      ggtitle(paste("Chart v Online. Function: ", f, ", guess rate: 1/", 1/g, sep = "" ))
      
    show(vaCO)
    
    vaLabOnline[row, 1] <- f
    vaLabOnline[row, 2] <- g
    vaLabOnline[row, 3] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$bias, digits = 2)
    vaLabOnline[row, 4] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$biasLowerCI, digits = 2)
    vaLabOnline[row, 5] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$biasUpperCI, digits = 2)
    vaLabOnline[row, 6] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$lowerLOA, digits = 2)
    vaLabOnline[row, 7] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$lowerLOA_lowerCI, digits = 2)
    vaLabOnline[row, 8] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$lowerLOA_upperCI, digits = 2)
    vaLabOnline[row, 9] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$upperLOA, digits = 2)
    vaLabOnline[row, 10] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$upperLOA_lowerCI, digits = 2)
    vaLabOnline[row, 11] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$upperLOA_upperCI, digits = 2)
    vaLabOnline[row, 12] <- round((sum(abs(blandr.statistics(d$Lab, d$Online, sig.level = p)$differences) > .2)/length(blandr.statistics(d$Lab, d$Online, sig.level = p)$differences))*100, digits = 2)
    vaLabOnline[row, 13] <- round((sum(abs(blandr.statistics(d$Lab, d$Online, sig.level = p)$differences) > .1)/length(blandr.statistics(d$Lab, d$Online, sig.level = p)$differences))*100, digits = 2)
    #vaLabOnline[row, 14] <- round(blandr.statistics(d$Lab, d$Online, sig.level = p)$upperLOA - blandr.statistics(d$Lab, d$Online, sig.level = p)$lowerLOA, digits = 2)
    
    vaLO <- blandr.draw(d$Lab, d$Online)+
      ggtitle(paste("Lab v Online. Function: ", f, ", guess rate: 1/", 1/g, sep = "" ))
      
    show(vaLO)
    
    
  }
  
}

vaChartOnline$ciDiff <- vaChartOnline$upperLOA - vaChartOnline$lowerLOA

```

We are basing the decision on the chart v online comparisons as this is most similar to what we want to use the test for
```{r plot final va}

vaStats <- data.frame(matrix(
  data = NA,
  ncol = 14,
  nrow =  3
))


names <- c("setting", "funciton", "guessRate",
           "bias", "biasLower", "biasUpper",
           "lowerLOA", "lowerLOA_lowerCI", "lowerLOA_upperCI",
           "upperLOA", "upperLOA_lowerCI", "upperLOA_upperCI",
           "point2diff", "point1diff")

colnames(vaStats) <- names

vaFinal <- va %>%
  filter(fun == "logistic_fun")%>%
  filter(gR == "26")

vaCO <- blandr.statistics(vaFinal$Chart, vaFinal$Online, sig.level = p)
vaCL <- blandr.statistics(vaFinal$Chart, vaFinal$Lab, sig.level = p)
vaLO <- blandr.statistics(vaFinal$Lab, vaFinal$Online, sig.level = p)


vaStats[1, 1] <- "chart v online"
vaStats[1, 2] <- "logistic_fun"
vaStats[1, 3] <- "26"
vaStats[1, 4] <- round(vaCO$bias, digits = 2)
vaStats[1, 5] <- round(vaCO$biasLowerCI, digits = 2)
vaStats[1, 6] <- round(vaCO$biasUpperCI, digits = 2)
vaStats[1, 7] <- round(vaCO$lowerLOA, digits = 2)
vaStats[1, 8] <- round(vaCO$lowerLOA_lowerCI, digits = 2)
vaStats[1, 9] <- round(vaCO$lowerLOA_upperCI, digits = 2)
vaStats[1, 10] <- round(vaCO$upperLOA, digits = 2)
vaStats[1, 11] <- round(vaCO$upperLOA_lowerCI, digits = 2)
vaStats[1, 12] <- round(vaCO$upperLOA_upperCI, digits = 2)
vaStats[1, 13] <- round((sum(abs(vaCO$differences) > .2)/length(vaCO$differences))*100, digits = 2)
vaStats[1, 14] <- round((sum(abs(vaCO$differences) > .1)/length(vaCO$differences))*100, digits = 2)

vaStats[2, 1] <- "chart v lab"
vaStats[2, 2] <- "logistic_fun"
vaStats[2, 3] <- "26"
vaStats[2, 4] <- round(vaCL$bias, digits = 2)
vaStats[2, 5] <- round(vaCL$biasLowerCI, digits = 2)
vaStats[2, 6] <- round(vaCL$biasUpperCI, digits = 2)
vaStats[2, 7] <- round(vaCL$lowerLOA, digits = 2)
vaStats[2, 8] <- round(vaCL$lowerLOA_lowerCI, digits = 2)
vaStats[2, 9] <- round(vaCL$lowerLOA_upperCI, digits = 2)
vaStats[2, 10] <- round(vaCL$upperLOA, digits = 2)
vaStats[2, 11] <- round(vaCL$upperLOA_lowerCI, digits = 2)
vaStats[2, 12] <- round(vaCL$upperLOA_upperCI, digits = 2)
vaStats[2, 13] <- round((sum(abs(vaCL$differences) > .2)/length(vaCL$differences))*100, digits = 2)
vaStats[2, 14] <- round((sum(abs(vaCL$differences) > .1)/length(vaCL$differences))*100, digits = 2)

vaStats[3, 1] <- "lab v online"
vaStats[3, 2] <- "logistic_fun"
vaStats[3, 3] <- "26"
vaStats[3, 4] <- round(vaLO$bias, digits = 2)
vaStats[3, 5] <- round(vaLO$biasLowerCI, digits = 2)
vaStats[3, 6] <- round(vaLO$biasUpperCI, digits = 2)
vaStats[3, 7] <- round(vaLO$lowerLOA, digits = 2)
vaStats[3, 8] <- round(vaLO$lowerLOA_lowerCI, digits = 2)
vaStats[3, 9] <- round(vaLO$lowerLOA_upperCI, digits = 2)
vaStats[3, 10] <- round(vaLO$upperLOA, digits = 2)
vaStats[3, 11] <- round(vaLO$upperLOA_lowerCI, digits = 2)
vaStats[3, 12] <- round(vaLO$upperLOA_upperCI, digits = 2)
vaStats[3, 13] <- round((sum(abs(vaLO$differences) > .2)/length(vaLO$differences))*100, digits = 2)
vaStats[3, 14] <- round((sum(abs(vaLO$differences) > .1)/length(vaLO$differences))*100, digits = 2)

vaMaxDiff <- max(c(max((vaCL$differences)), max((vaCO$differences)), max((vaLO$differences))  ) )+0.01
vaMinDiff <- min(c(min((vaCL$differences)), min((vaCO$differences)), min((vaLO$differences))  ) )-0.05

vaMaxMean <- max(c(max((vaCL$means)), max((vaCO$means)), max((vaLO$means))  ) )
vaMinMean <- min(c(min((vaCL$means)), min((vaCO$means)), min((vaLO$means))  ) )

# order = Chart v OU, Chart v OSS, OSS v OU
# order of areas to be shaded - bias, lower CI upper CI
vaXmin <- -Inf
vaXmax <- Inf



vaCO_BA <- blandr.draw(vaFinal$Chart, vaFinal$Online,
                       ciShading = FALSE, ciDisplay=TRUE, plotter = "ggplot")+
  ylim(vaMinDiff, vaMaxDiff)+
  xlim(vaMinMean, vaMaxMean)+
  theme_bw()+ 
  theme(
    plot.title = element_blank()
    )+ 
  geom_rect(aes(xmin= vaXmin, xmax= vaXmax, ymin= vaCO$biasLowerCI, ymax= vaCO$biasUpperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= vaXmin, xmax= vaXmax, ymin= vaCO$lowerLOA_lowerCI, ymax= vaCO$lowerLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= vaXmin, xmax= vaXmax, ymin= vaCO$upperLOA_lowerCI, ymax= vaCO$upperLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)

vaCL_BA <- blandr.draw(vaFinal$Chart, vaFinal$Lab,
                       ciShading = FALSE, ciDisplay=TRUE, plotter = "ggplot")+
  ylim(vaMinDiff, vaMaxDiff)+
  xlim(vaMinMean, vaMaxMean)+
  theme_bw()+
  theme(
    plot.title = element_blank()
    )+ 
  geom_rect(aes(xmin= vaXmin, xmax= vaXmax, ymin= vaCL$biasLowerCI, ymax= vaCL$biasUpperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= vaXmin, xmax= vaXmax, ymin= vaCL$lowerLOA_lowerCI, ymax= vaCL$lowerLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= vaXmin, xmax= vaXmax, ymin= vaCL$upperLOA_lowerCI, ymax= vaCL$upperLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)

vaLO_BA <- blandr.draw(vaFinal$Lab, vaFinal$Online,
                       ciShading = FALSE, ciDisplay=TRUE, plotter = "ggplot")+
  ylim(vaMinDiff, vaMaxDiff)+
  xlim(vaMinMean, vaMaxMean)+
  theme_bw()+
  theme(
    plot.title = element_blank()
    )+ 
  geom_rect(aes(xmin= vaXmin, xmax= vaXmax, ymin= vaLO$biasLowerCI, ymax= vaLO$biasUpperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= vaXmin, xmax= vaXmax, ymin= vaLO$lowerLOA_lowerCI, ymax= vaLO$lowerLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)+ 
  geom_rect(aes(xmin= vaXmin, xmax= vaXmax, ymin= vaLO$upperLOA_lowerCI, ymax= vaLO$upperLOA_upperCI), 
            fill = "grey50",
            alpha = 0.02)
vaXlab <- "Mean VA score (logMAR)"

vaPlot <- ggarrange(
  vaCO_BA + ylab("Clinical v OU \n VA score difference (logMAR)")+ 
    theme(axis.title.x = element_blank(), plot.margin = unit(margins, 'lines')), 
  vaCL_BA + ylab("Clinical v OSS \n VA score difference (logMAR)")+ 
    theme(axis.title.x = element_blank(), plot.margin = unit(margins, 'lines')), 
  vaLO_BA + xlab(vaXlab) + ylab("OSS v OU \n VA score difference (logMAR)")+ 
    theme(plot.margin = unit(bottomMargin, 'lines')),
          ncol = 1,
          labels = c("A", "B", "C"),
          align = "hv")

show(vaPlot)

```

```{r plot params}

h = 20
w = (h/4)*3
d = 300
```

# save plots
```{r save plots, eval = FALSE}

#### submission plots
ggsave(paste("../figures/SUBMISSION/figure1.tiff", sep = ""), 
       plot = csPlot, dpi = d,units = 'cm', height = h, width = w)

ggsave(paste("../figures/SUBMISSION/figure2.tiff", sep = ""), 
       plot = vaPlot, dpi = d,units = 'cm', height = h, width = w)
```

Check order effects
```{r order effects}

order = read.csv("../data/sessionOrder.csv")

csOrder <- left_join(csFinal, order, by = "id") %>%
  select(id, Lab, Online, onlineFirst) %>%
  mutate(first = case_when(
    onlineFirst == 1 ~ Online,
    TRUE ~ Lab
  ),
  second = case_when(
    onlineFirst == 0 ~ Online, 
    TRUE ~ Lab
  )
  )

vaOrder <- left_join(vaFinal, order, by = "id") %>%
  select(id, Lab, Online, onlineFirst)%>%
  mutate(first = case_when(
    onlineFirst == 1 ~ Online,
    TRUE ~ Lab
  ),
  second = case_when(
    onlineFirst == 0 ~ Online, 
    TRUE ~ Lab
  )
  )

csOrder %>%
  group_by(onlineFirst) %>%
  summarise(Online = mean(Online),
            Lab = mean(Lab))

wilcox.test(csOrder$first, csOrder$second, paired = TRUE, alternative = "two.sided")

vaOrder %>%
  group_by(onlineFirst) %>%
  summarise(Online = mean(Online),
            Lab = mean(Lab))

wilcox.test(vaOrder$first, vaOrder$second, paired = TRUE, alternative = "two.sided")

```


