---
title: "Exp 2 Data Screening"
author: "Will Sheppard"
date: "2023-08-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This function takes a list of the required packages, checks if they are installed, downloads those that are not, and then loads them.

```{r packages, warning=FALSE}

requiredPackages = c("tidyverse")
for(p in requiredPackages){
  if(!require(p,character.only = TRUE)) install.packages(p)
  library(p,character.only = TRUE)
}

```

Lets own load the data. Here we need researcher Qs, headingPerception_demographics, chart test and the online vision tests data
```{r import data}

setwd("../dataExp2")

resQ <- NA
demo <- NA
chartTest <- NA
visT <- NA
visTest <- NA
visTestAll <- NA

# researcher Qs - pattern dk24.csv
(resQfiles <- list.files(pattern = "dk24.csv"))
for (file in resQfiles) {
  d <- read.csv(file = file)%>%
    select(Participant.Private.ID, ppID, sessionNumber, condition)

  resQ <- rbind(resQ, d)
}

# demographics pattern e2l7.csv
(demofiles <- list.files(pattern = "e2l7.csv"))
for (file in demofiles) {
  d <- read.csv(file = file)

  demo <- rbind(demo, d)%>%
    filter(Event.Index != "END OF FILE")
}

# Chart test - pattern = b7ag.csv
(chartfiles <- list.files(pattern = "b7ag.csv"))
for (file in chartfiles) {
  d <- read.csv(file = file)%>%
    filter(Zone.Name == "Zone1")%>%
    select(Participant.Private.ID, display, Response)%>%
    pivot_wider(id_cols = Participant.Private.ID, values_from = Response, names_from = display)

  chartTest <- rbind(chartTest, d)
}

# for the vision tests we have 10 patterns, so we will need to double for loop it
# dqjp, z5dj, og71, mva3, oex3, d4fw, f3ud, rek9, svji, s8ch
visPats <- c("dqjp.csv", "z5dj.csv", "og71.csv", "mva3.csv", "oex3.csv", "d4fw.csv", "f3ud.csv", "rek9.csv", "svji.csv", "s8ch.csv")
vis <- c("cs", "va")

for (pat in visPats) {
  (visFiles <- list.files(pattern = pat))
  for (file in visFiles) {
    d <- read.csv(file = file)
    
    visT <- rbind(visT, d)
  }
  
  visTestAll <- rbind(visTestAll, visT)
  
}

visTest <- visTestAll %>%
  filter(display %in% vis) %>%
  filter(Response.Type == "Enter Key")

ACQ <- visTestAll %>%
  filter(display == "ACQ") %>%
  filter(Response.Type == "Enter Key") %>%
  select(Participant.Private.ID, ACQ, ACQ_answer, Response, Correct)

```

now we need to select the younger participants

Participant 6 and 7 have an extra session, need to figure out which ones these are
```{r young pps}

resQ <- resQ %>%
  filter(ppID < 17)
idsFirst <- c(8112487, 8113028, 8055867, 8056577) # ids of doubled sessions

# no chart test for 8055867, remove. 8056577, retain
sixNsevChart <- chartTest %>%
  filter(Participant.Private.ID %in% idsFirst)

idsSecond <- c(8112487, 8113028)

sixNsevVis <- visTest %>%
  filter(Participant.Private.ID %in% idsSecond)

unique(sixNsevVis$Participant.Private.ID) # 8112487, remove. 8113028, retain

remove <- c(8055867, 8112487)
```

let's remove these participants from the data frames.
```{r remove errant pps}
resQ <- subset(resQ, !(Participant.Private.ID %in% remove))
ACQ <- subset(ACQ, !(Participant.Private.ID %in% remove))
demo <- subset(demo, !(Participant.Private.ID %in% remove))
visTest <- subset(visTest, !(Participant.Private.ID %in% remove))
```

Lets merge the resQ df into the other the dfs
files get shorter as this will remove the older pps too
```{r merge res Q}
ACQ <- merge(resQ, ACQ, by = "Participant.Private.ID")
demo <- merge(resQ, demo, by = "Participant.Private.ID")
visTest <- merge(resQ, visTest, by = "Participant.Private.ID")
```

Quick ACQ check - no incorrect answers
WOOOPPP
```{r ACQ check}

wrongACQ <- ACQ %>%
  filter(Correct == 0)
```

DOBs
particpant 7 down as 14 months old - actually 253
```{r DOBs}
demo$dob.inmonths <- replace(demo$dob.inmonths, demo$dob.inmonths == 14, 253)

min(demo$dob.inmonths)/12
max(demo$dob.inmonths)/12
mean(demo$dob.inmonths)/12
sd(demo$dob.inmonths)/12
```

lets look at the gender split
```{r gender}
table(demo$sex)

```

hoe about handedness
```{r hand}

table(demo$Handedness)
```
